---
title: "University of Alberta Faculty of Engineering Research Output"
author: "Alison Henry"
date: "October 27, 2017"
output:
 word_document:
                df_print: kable
bibliography: ROA2017.bib
csl: chemical-engineering-journal.csl
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE, message = FALSE, warning  = FALSE)
```
A report to examine the publication output of the Univeristy of Alberta Faculty of Engineering. Searches were conducted using Web of Science, and limited to the five publication years from 2012-2016. 

```{r package installation}
##Install and load needed packages

##install.packages("bibliometrix", dependencies = TRUE)
##install.packages("splitstackshape")
##install.packages("tidyverse")
##install.packages("viridis")
##install.packages("knitr")

library(bibliometrix)
library(splitstackshape)
library(tidyverse)
library(stringr)
library(viridis)
library(knitr)
```
Initial processing of the data was accomplished with the Bibliometrix package written by Massimo Aria and Corrado Cuccurullo[@RefWorks:doc:59d24e48e4b0b590b97a2290]. This allowed easy conversion of records into a data frame to facilitate further processing.

```{r data import}
## read in U15 publication data from previous process, add school name column to each
Alberta <- read.csv("Alberta.csv", sep = ",")
Alberta$PY <- as.factor(Alberta$PY)
Alberta$School <- "Alberta"
Alberta$School <- as.factor(Alberta$School)

Calgary <- read.csv("Calgary.csv", sep = ",")
Calgary$PY <- as.factor(Calgary$PY)
Calgary$School <- "Calgary"
Calgary$School <- as.factor(Calgary$School)

Dalhousie <- read.csv("Dalhousie.csv", sep = ",")
Dalhousie$PY <- as.factor(Dalhousie$PY)
Dalhousie$School <- "Dalhousie"
Dalhousie$School <- as.factor(Dalhousie$School)

Laval <- read.csv("Laval.csv", sep = ",")
Laval$PY <- as.factor(Laval$PY)
Laval$School <- "Laval"
Laval$School <- as.factor(Laval$School)

Manitoba <- read.csv("Manitoba.csv", sep = ",")
Manitoba$PY <- as.factor(Manitoba$PY)
Manitoba$School <- "Manitoba"
Manitoba$School <- as.factor(Manitoba$School)

McGill <- read.csv("McGill.csv", sep = ",")
McGill$PY <- as.factor(McGill$PY)
McGill$School <- "McGill"
McGill$School <- as.factor(McGill$School)

McMaster <- read.csv("McMaster.csv", sep = ",")
McMaster$PY <- as.factor(McMaster$PY)
McMaster$School <- "McMaster"
McMaster$School <- as.factor(McMaster$School)

Ottawa <- read.csv("Ottawa.csv", sep = ",")
Ottawa$PY <- as.factor(Ottawa$PY)
Ottawa$School <- "Ottawa"
Ottawa$School <- as.factor(Ottawa$School)

Montreal <- read.csv("Montreal.csv", sep = ",")
Montreal$PY <- as.factor(Montreal$PY)
Montreal$School <- "Montreal"
Montreal$School <- as.factor(Montreal$School)

Queens <- read.csv("Queens.csv", sep = ",")
Queens$PY <- as.factor(Queens$PY)
Queens$School <- "Queens"
Queens$School <- as.factor(Queens$School)

Saskatchewan <- read.csv("Saskatchewan.csv", sep = ",")
Saskatchewan$PY <- as.factor(Saskatchewan$PY)
Saskatchewan$School <- "Saskatchewan"
Saskatchewan$School <- as.factor(Saskatchewan$School)

Toronto <- read.csv("Toronto.csv", sep = ",")
Toronto$PY <- as.factor(Toronto$PY)
Toronto$School <- "Toronto"
Toronto$School <- as.factor(Toronto$School)

UBC <- read.csv("UBC.csv", sep = ",")
UBC$PY <- as.factor(UBC$PY)
UBC$School <- "UBC"
UBC$School <- as.factor(UBC$School)

Waterloo <- read.csv("Waterloo.csv", sep = ",")
Waterloo$PY <- as.factor(Waterloo$PY)
Waterloo$School <- "Waterloo"
Waterloo$School <- as.factor(Waterloo$School)

Western <- read.csv("Western.csv", sep = ",")
Western$PY <- as.factor(Western$PY)
Western$School <- "Western"
Western$School <- as.factor(Western$School)

```

